Best Practices for Multiple Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-05-15 paper/manuscript.tex
add kartograf sentence

Methods from experimental design have been applied to the construction of perturbation maps. Yang et al.~\cite{yang2020optimal} showed how to optimize the perturbation map by selecting a fixed number of calculations from the pairwise perturbations so that the resulting set of calculations minimize the total variance. Xu~\cite{xu2019optimal} showed how to optimize the perturbation map by allocating different amounts of simulation time to different pairwise perturbations so as to minimize the total variance, given the total simulation time of all the perturbation calculations. Both approaches lead to substantial reduction in the statistical error of the estimated free energies.

>>>>

Methods from experimental design have been applied to the construction of perturbation maps. Several styles of network designs have been proposed in recent years, although no single method seems to consistently outperform all others.\cite{KARTOGRAF} Yang et al.~\cite{yang2020optimal} showed how to optimize the perturbation map by selecting a fixed number of calculations from the pairwise perturbations so that the resulting set of calculations minimize the total variance. Xu~\cite{xu2019optimal} showed how to optimize the perturbation map by allocating different amounts of simulation time to different pairwise perturbations so as to minimize the total variance, given the total simulation time of all the perturbation calculations. Both approaches lead to substantial reduction in the statistical error of the estimated free energies.
